Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-12 ppdp24/examples.tex
checkpoint

@@

\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then:
  $$
  \condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {\{ \elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}
  $$
  $$
  \conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}    
  $$
\end{lemma}

>>>>

\begin{definition}
  For all $\alpha \in \{ \mesg{w}, \flip{w} \}$ define:
  $$\pmf(\macgv{\alpha} = v) \defeq \sum_{\sigma) \in A} \pmf(\sigma')$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\alpha} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \pmf(\sigma \cap \sigma')/\pmf(\sigma')$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\alpha}{1}) + \store(\elab{\alpha}{2})} = v \}$.
\end{definition}

@@

\begin{lemma}
  If $\condsep{\pmf}{X_1}{X_2}{X_3}$ and
  $\condp{\pmf}{X_2}{\detx{X_4}}$ then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
\end{lemma}

\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then:
  $$
  \condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {\{ \elab{\mesg{x}}{2},\elab{\mesg{y}}{2},\elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}
  $$
  $$
  \conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}    
  $$
\end{lemma}
